---
title: "p8105_hw1_ars2376"
author: ars2376
output: html_document
date: "2025-09-12"
---

**Problem 1**

```{r setup}
library(moderndive)
library(tidyverse)
```

```{r}
data("early_january_weather")
?early_january_weather
nrow(early_january_weather)
ncol(early_january_weather)
mean(early_january_weather$temp)
```
The dataset `early_january_weather` contains the hourly meteorological data for LGA, JFK, and EWR for the month of January 2013. It has 358 rows or hourly measurements and 15 columns or variables. Variables in this dataset are the weather station (`origin`), time of recording (`year`, `month`, `day`, `hour`), temperature in F (`temp`), dewpoint in F (`dewp`), relative humidity (`humid`), wind direction in degrees (`wind_dir`), wind speed in mph (`wind_speed`), gust speed in mph (`wind_gust`), precipitation in inches (`precip`), sea level pressure in millibars (`pressure`), visibility in miles (`visib`), and date and hour of the recording (`time_hour`). Using `temp`, the average temperature in January 2013 was found to be 39.58 degrees F.

```{r yx_scatter}
jan_weather_scatterplot <- early_january_weather |>
  ggplot(aes(x = time_hour, y = temp, color = humid)) +
    geom_point(alpha = .5) +
  labs(
    title = "Temperature in January 2013",
    x = "Date and hour of recording",
    y = "Temperature in Fahrenheiht",
    color = "Relative Humidity"
  )
```

The scatterplot displays a cyclical pattern, representing temperatures increasing during the day then cooling down in the evening. Throughout the month, the average temperature is shown to be steadily increasing. Higher relative humidity is also associated with higher temperature.

```{r}
ggsave("jan_weather_scatterplot.png", height = 5, width = 7)
```

**Problem 2**

```{r}
weather_df = tibble(
  x = rnorm(10),
  log_vector = x > 0,
  char_vector = c("My", "name", "is", "Amanda", "and", "I", "am", "enrolled", "in", "P8105"),
  factor_vector = factor(sample(c("a", "b", "c"), 10, replace = TRUE))
)
```

```{r}
weather_df %>%
  pull(x) %>%
  mean(na.rm=TRUE)

weather_df %>%
  pull(log_vector) %>%
  mean(na.rm=TRUE)

weather_df %>%
  pull(char_vector) %>%
  mean(na.rm=TRUE)

weather_df %>%
  pull(factor_vector) %>%
  mean(na.rm=TRUE)
``` 

I am able to take the mean of the random sample `x` and logical vector `log_vector` but not of the character vector `char_vector` and factor vector `factor_vector`. This is due to `x` and `log_vector` being numeric variables while the other 2 are string variables, which we cannot take the mean of.

```{r,results="hide", warning=FALSE}
as.numeric(weather_df$log_vector)
as.numeric(weather_df$char_vector)
as.numeric(weather_df$factor_vector)
```

The `as.numeric` function changes the logical variable from `TRUE` to `1` and `FALSE` to `0` since coercion makes logical variables automatically become numeric. This explains why we were able to take the mean. For the character variable, values are all changed to `NA` and we get the warning `NAs introduced by coercion` since there are no meaningful numeric values, even after coercion. This explains why no mean could be taken. For the factor variable, `a` is changed to `1`, `b` is changed to `2`, and `c` is changed to `3`, their underlying integer codes. However, we were still unable to take the mean because the factor levels didn't have numeric measures originally.