---
title: "p8105_hw1_ars2376"
author: ars2376
output: html_document
date: "2025-09-12"
---

**Problem 1**

```{r setup, include = false}
library(moderndive)
```

```{r}
data("early_january_weather")
?early_january_weather
nrow(early_january_weather)
ncol(early_january_weather)
mean(early_january_weather$temp)
```
The dataset `early_january_weather` contains the hourly meteorological data for LGA, JFK, and EWR for the month of January 2013. It has 358 rows and 15 columns. Variables in this dataset are the weather station (`origin`), time of recording (`year`, `month`, `day`, `hour`), temperature in F (`temp`), dewpoint in F (`dewp`), relative humidity (`humid`), wind direction in degrees (`wind_dir`), wind speed in mph (`wind_speed`), gust speed in mph (`wind_gust`), precipitation in inches (`precip`), sea level pressure in millibars (`pressure`), visibility in miles (`visib`), and date and hour of the recording (`time_hour`). Using `temp`, the average temperature in January 2013 was found to be 39.58 degrees F.

**Problem 2**